---
title: "Math 168A Homework 1"
output: pdf_document
---
## Austin Clark A91063616


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
First we create a function that takes a given probability p and outputs a vector of the results of 
a random walk of length 100 with a given probability p. For each step of this function it chooses 1 with 
probability p and -1 with probability 1-p and then sums the total.
```{r}
random_walk <- function(p){
  v = c(1,-1)
  x = numeric(100)
  count = 0
  p2 <-c(p, 1-p)
  for( i in 1:100){
    count = count + sample(v,size = 1, replace = TRUE, prob = p2 )
    x[i]= count
  }
  return(x)
}
```

The following Plots are the results of 100 steps of a random walk with probabilitys .4, .5, .6 respectivelly

```{r, echo=FALSE, fig.width=6, fig.height=4}

prob_1 <- random_walk(.4)
plot.ts(prob_1, xlab = "time", ylab = "", main = "p= .4")
prob_2 <- random_walk(.5) 
plot.ts(prob_2,  xlab= "time", ylab = "",main = "p= .5")
prob_3 <- random_walk(.6)
plot.ts(prob_3,  xlab= "time", ylab = "",main = "p= .6")

```

Next we write a function to get the final position of 100 steps of a random walk with a given probability 500 times

```{r}
many_walks = function(p){
  x = numeric(500)
  for( i in 1:500){
    hold = random_walk(p)
    x[i]= hold[100]
  }
  return(x)
}
```

Here are the results of the above function in a histogram with probabilities .4, .5, .6


```{r, echo=FALSE, fig.width=6, fig.height=5}
Mwalks_1= many_walks(.4)
hist(Mwalks_1,breaks = 70,xlab = "final position", main = "500 walks p= .4")
paste("The mean with a probability of .4 is ", mean(Mwalks_1))
paste("The variance is ", var(Mwalks_1))

Mwalks_2 = many_walks(.5)
hist(Mwalks_2,breaks = 70,xlab = "final position", main = "500 walks p= .5")
paste("The mean with a probability of .5 is ", mean(Mwalks_2))
paste("The variance is ", var(Mwalks_2))

Mwalks_3 <-many_walks(.6)
hist(Mwalks_3,breaks = 70,xlab = "final position", main = "500 walks p= .6")
paste("The mean with a probability of .4 is ", mean(Mwalks_3))
paste("The variance is ", var(Mwalks_3))

```

Note that the mean changes based on the probability but the variance does not necessarily change











